\section{Publication}\label{publication}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{Sunghyun Kim}, Ji-Sang Park, Samantha N. Hood, and Aron Walsh,
  \textbf{``Lone-pair effect on carrier capture in
  \(\mathrm{Cu_{2}ZnSnS_{4}}\) solar cells''}
  \href{https://pubs.rsc.org/en/content/articlelanding/2019/ta/c8ta10130b}{J.
  Mater. Chem. A, 7, 2686 (2019)}
\item
  Ji-Sang Park, \textbf{Sunghyun Kim}, Samantha N. Hood, and Aron Walsh,
  \textbf{``Open-circuit voltage deficit in \(\mathrm{Cu_{2}ZnSnS_{4}}\)
  solar cells by interface bandgap narrowing''}
  \href{https://aip.scitation.org/doi/abs/10.1063/1.5063793}{Appl. Phys.
  Lett. 113, 212103 (2018)}
\item
  Ji-Sang Park, \textbf{Sunghyun Kim}, and Aron Walsh,
  \textbf{``Stability and electronic properties of planar defects in
  quaternary I2-II-IV-VI4 semiconductors''}
  \href{https://doi.org/10.1063/1.5053424}{J. Appl. Phys. 124 165705
  (2018)}
\item
  MinJoong Kim, \textbf{Sunghyun Kim}, Dong Hoon Song, Se Kwon Oh, Kee
  Joo Chang, and Eun Ae Cho, \textbf{``Promotion of electrochemical
  oxygen evolution reaction by chemical coupling of cobalt to molybdenum
  carbide''} \href{https://doi.org/10.1016/j.apcatb.2018.01.051}{Appl.
  Catal. B 227, 340 (2018)}
\item
  Ji-Sang Park, \textbf{Sunghyun Kim}, Zijuan Xie, and Aron Walsh,
  \textbf{``Point defect engineering in thin-film solar cells''},
  \href{https://doi.org/10.1038/s41578-018-0026-7}{Nat. Rev.~Mat. 3, 194
  (2018)}
\item
  Bartomeu Monserrat, Ji-Sang Park, \textbf{Sunghyun Kim} and Aron
  Walsh, \textbf{``Role of electron-phonon coupling and thermal
  expansion on band gaps, carrier mobility, and interfacial offsets in
  kesterite thin-film solar cells''},
  \href{https://doi.org/10.1063/1.5028186}{Appl. Phys. Lett. 112, 193903
  (2018)}
\item
  \textbf{Sunghyun Kim}, Ji-Sang Park, and Aron Walsh,
  \textbf{``Identification of Killer Defects in Kesterite Thin-Film
  Solar Cells''},
  \href{https://pubs.acs.org/doi/abs/10.1021/acsenergylett.7b01313}{ACS
  Energy Lett. 3, 496 (2018)}
\item
  Ji-Sang Park, \textbf{Sunghyun Kim}, and Aron Walsh,
  \textbf{``Opposing effects of stacking faults and antisite domain
  boundaries on the conduction band edge in kesterite quaternary
  semiconductors''}
  \href{https://journals.aps.org/prmaterials/abstract/10.1103/PhysRevMaterials.2.014602}{Phys.
  Rev.~Mat. 2, 014602 (2018)}
\item
  Woo Hyun Han, \textbf{Sunghyun Kim}, In-Ho Lee, and K. J. Chang,
  \textbf{``Prediction of Green Phosphorus with Tunable Direct Band Gap
  and High Mobility''},
  \href{https://pubs.acs.org/doi/10.1021/acs.jpclett.7b02153}{J. Phys.
  Chem. Lett. 8, 4627(2017)}
\item
  \textbf{Sunghyun Kim}, Woo Hyun Han, In-Ho Lee, and K. J. Chang,
  \textbf{``Discovery of Half-Metallic Two-Dimensional Boron Kagome
  Lattice through Material Design''},
  \href{https://www.nature.com/articles/s41598-017-07518-9}{Scientific
  Reports 7, 7279 (2017)}
\item
  Ha-Jun Sung, \textbf{Sunghyun Kim}, In-Ho Lee, and K. J. Chang,
  \textbf{``Semimetallic carbon allotrope with topological nodal line in
  mixed sp\(^3\)-sp\(^2\) bonding networks''}
  \href{http://www.nature.com/am/journal/v9/n3/full/am201726a.html}{NPG
  Asia Materials 9, e361 (2017)}
\item
  Woo Hyun Han, Young Jun Oh, Duk-Hyun Choe, \textbf{Sunghyun Kim},
  In-Ho Lee and Kee Joo Chang, \textbf{``Three-dimensional buckled
  honeycomb boron lattice with vacancies as an intermediate phase on the
  transition pathway from \(\alpha\)-B to \(\gamma\)-B''}
  \href{http://www.nature.com/am/journal/v9/n7/full/am201798a.html}{NPG
  Asia Materials 9, e400 (2017)}
\item
  Elisabeth Pratidhina, \textbf{Sunghyun Kim}, and K. J. Chang,
  \textbf{``Design of Dipole-Allowed Direct Band Gaps in Ge/Sn
  Core--Shell Nanowires''},
  \href{http://pubs.acs.org/doi/abs/10.1021/acs.jpcc.6b08779}{J. Phys.
  Chem. C 120, 28169 (2016)}
\item
  In-Ho Lee, Young Jun Oh, \textbf{Sunghyun Kim}, Jooyoung Lee, and K.
  J. Chang, \textbf{``Ab initio materials design using conformational
  space annealing and its application to searching for direct band gap
  silicon crystals''},
  \href{http://dx.doi.org/10.1016/j.cpc.2016.02.011}{Comp. Phys. Comm.
  203, 110 (2016).}
\item
  Young Jun Oh, \textbf{Sunghyun Kim}, In-Ho Lee, Jooyoung Lee, and K.
  J. Chang, \textbf{``Direct band gap carbon superlattices with
  efficient optical transition''},
  \href{http://journals.aps.org/prb/abstract/10.1103/PhysRevB.93.085201}{Phys.
  Rev.~B 93, 085201 (2016).}
\item
  Young Jun Oh, In-Ho Lee, \textbf{Sunghyun Kim}, Jooyoung Lee, and K.
  J. Chang, \textbf{``Dipole-allowed direct band gap silicon
  superlattices''}, \href{http://dx.doi.org/10.1038/srep18086}{Sci.
  Rep.~8, 18086 (2015).}
\item
  In-Ho Lee, Jooyoung Lee, Young Jun Oh, \textbf{Sunghyun Kim}, and K.
  J. Chang, \textbf{``Computational search for direct band gap silicon
  crystals''},
  \href{http://journals.aps.org/prb/abstract/10.1103/PhysRevB.90.115209}{Phys.
  Rev.~B 90, 115209 (2014).}
\item
  \textbf{Sunghyun Kim}, Ji-Sang Park, and K. J. Chang,
  \textbf{``Finite-size supercell correction scheme for charged defects
  in one-dimensional systems''},
  \href{http://journals.aps.org/prb/abstract/10.1103/PhysRevB.90.085435}{Phys.
  Rev.~B 90, 085435 (2014).}
\item
  \textbf{Sunghyun Kim}, Ji-Sang Park, K. J. Chang, \textbf{``Stability
  and Segregation of B and P Dopants in Si/SiO\(_2~\) Core--Shell
  Nanowires''},
  \href{http://pubs.acs.org/doi/abs/10.1021/nl3013924}{Nano lett. 12,
  5068 (2012).}
\end{enumerate}
