\section{Selected Publications}\label{selected-publications}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Sunghyun Kim}, Ji-Sang Park, Samantha N. Hood, and Aron Walsh,
  \textbf{``Lone-pair effect on carrier capture in
  \(\boldsymbol{\mathrm{Cu_{2}ZnSnS_{4}}}\) solar cells''}
  \href{https://pubs.rsc.org/en/content/articlelanding/2019/ta/c8ta10130b}{J.
  Mater. Chem. A, 7, 2686 (2019)}

  \begin{itemize}
  \tightlist
  \item
    I contributed to the formulation of the problem, theoretical
    calculations, and the preparation of the manuscript. I wrote the
    program package to solve the program.
  \end{itemize}
\item
  Ji-Sang Park, \textbf{Sunghyun Kim}, Zijuan Xie, and Aron Walsh,
  \textbf{``Point defect engineering in thin-film solar cells''},
  \href{https://doi.org/10.1038/s41578-018-0026-7}{Nat. Rev.~Mat. 3, 194
  (2018)}

  \begin{itemize}
  \tightlist
  \item
    I researched data for the article and contributed to the discussion
    of content and the preparation of the manuscript.
  \end{itemize}
\item
  \textbf{Sunghyun Kim}, Ji-Sang Park, and Aron Walsh,
  \textbf{``Identification of Killer Defects in Kesterite Thin-Film
  Solar Cells''},
  \href{https://pubs.acs.org/doi/abs/10.1021/acsenergylett.7b01313}{ACS
  Energy Lett. 3, 496 (2018)}

  \begin{itemize}
  \tightlist
  \item
    I contributed to the formulation of the problem, theoretical
    calculations, and the preparation of the manuscript.
  \end{itemize}
\item
  \textbf{Sunghyun Kim}, Woo Hyun Han, In-Ho Lee, and K. J. Chang,
  \textbf{``Discovery of Half-Metallic Two-Dimensional Boron Kagome
  Lattice through Material Design''},
  \href{https://www.nature.com/articles/s41598-017-07518-9}{Scientific
  Reports 7, 7279 (2017)}

  \begin{itemize}
  \tightlist
  \item
    I contributed to the formulation of the problem, theoretical
    calculations, and the preparation of the manuscript. I wrote the
    program package to solve the program.
  \end{itemize}
\item
  \textbf{Sunghyun Kim}, Ji-Sang Park, and K. J. Chang,
  \textbf{``Finite-size supercell correction scheme for charged defects
  in one-dimensional systems''},
  \href{http://journals.aps.org/prb/abstract/10.1103/PhysRevB.90.085435}{Phys.
  Rev.~B 90, 085435 (2014).}

  \begin{itemize}
  \tightlist
  \item
    I contributed to the formulation of the problem, theoretical
    calculations, and the preparation of the manuscript. I wrote the
    program package to solve the program.
  \end{itemize}
\end{enumerate}
